---
title: "Poverty Report"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source("Aggregate.r")
source("Summary Information Script.R")
source("char1.R")
source("char2.R")
```

# Exploratory Analysis of U.S. Poverty Data
We're really interested in how poverty changes over time in the U.S.
Some questions we hope to answer are:

1. How has poverty changed over the course of 10 years?
2. How has race played a factor in this?
3. How has the coronavirus increased the gap between the poor and the rich?

The datasets we chose for this exploratory analysis are from the US Census (irs.csv) and Kaggle (covid_data_log_200822.csv). Based on our script, we found out that the data was taken over the course of 30 years; from 1989 to 2018. We were also curious on how the average of both the total exemption amount and specifically the poor exemption amount changed over time. Thus, we created two new tables calculating each variable for each year, and we found out that the average for both have overall increased as time went on. 

## Data Summary Information















### Chart 1
```{r echo=F}
poor_exemption_over_year

```



#### Chart 2
```{r echo = F}
chart2

```


##### Chart 3
```{r echo = F}


```